---
title: "Email Graph"
author: "Bill"
date: '2022-08-16'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(igraph)
library(dplyr)
```

We read in the email graph data.

```{r}
emails = read.csv('email-Eu-core.txt', sep = ' ' , header = FALSE)

drop_rows <- c()
for(r in 1:nrow(emails)){
  if(emails[r,1] == emails[r,2]){
    drop_rows <- c(drop_rows, r)
  }
}
emails <- emails[-drop_rows,]

head(emails)

rm(drop_rows)
```

We investigate the current node names.

```{r}
nodes <- sort(union(emails[,1], emails[,2]))
head(nodes)
tail(nodes)
length(nodes)
```

We see the nodes are named 0 to 1004 inclusive. To generate a graph from this data we simply add one to each of the node names.

```{r}
nodes <- nodes + 1
emails <- emails + 1
email_graph <- graph_from_edgelist(as.matrix(emails), directed = F)
```

And we check the adjacency has the right size.

```{r}
dim(get.adjacency(email_graph))
rm(email_graph)
```

Great, we are now ready to take samples from this graph. We start by assigning the nodes into 5 groups.

```{r}
nodes <- sample(nodes)
chunk_number <- 5
assignment <- data.frame(rep_len(1:chunk_number, length(nodes)))
row.names(assignment) <- nodes
```

```{r}
primes <- c(2,3,5,7,11,13,17)
```

```{r}
emails <- emails %>% mutate(key = primes[assignment[as.character(V1), 1]] * primes[assignment[as.character(V2), 1]])

emails <- emails %>% mutate(graph = 0)
```

```{r}
for(g in 1:chunk_number){
  for(r in 1:nrow(emails)){
    if(emails[r, 3] %% primes[g] == 0 & emails[r, 3] < (primes[g] ** 2) + 1 &
       emails[r, 4] == 0){
      emails[r,4] = g
    }
    if(emails[r, 3] %% primes[g] == 0 & emails[r, 4] == 0 &
       sample(c(T, F), size = 1)){
      emails[r,4] = g
    }
  }
}
rm(g, r, chunk_number)
```

```{r}
table(emails[, 4])
```

Need some chunk which adjusts the edges to external nodes to single nodes.

```{r}
sub_edge_list <- emails[emails$graph == 1,]

for(r in 1:nrow(sub_edge_list)){
  if(assignment[as.character(sub_edge_list[r,1]), 1] != 1){
    sub_edge_list[r, 1] = 
      assignment[as.character(sub_edge_list[r,1]), 1] + 2000
  }
  if(assignment[as.character(sub_edge_list[r,2]), 1] != 1){
    sub_edge_list[r, 2] = 
      assignment[as.character(sub_edge_list[r,2]), 1] + 2000
  }
}

sub_edge_list <- sub_edge_list[,1:2]

rm(r)
```

Then the standard fix for generating graphs with non-consecutive node names.

```{r}
sub_nodes <- union(sub_edge_list[,1], sub_edge_list[,2])
length(sub_nodes)

new_names <- data.frame(1:length(sub_nodes))
row.names(new_names) <- sub_nodes

sub_edge_list <- sub_edge_list %>% mutate(V1 = new_names[as.character(V1),1])
sub_edge_list <- sub_edge_list %>% mutate(V2 = new_names[as.character(V2),1])

union(sub_edge_list[,1], sub_edge_list[,2])

rm(new_names, sub_nodes)
```

Great, this has worked. We generate the graph.

```{r}
subgraph <- graph_from_edgelist(as.matrix(sub_edge_list), directed = F)
```
